Hierarchical Reverberation Mapping

### 2013-10-27 Paper/ms.tex
New figure
Working on ccf and figs

\begin{abstract}
Reverberation mapping (RM) is an important technique in studies of active
galactic nuclei (AGN). The key idea of RM is to measure the time lag $\tau$
between variations in the continuum emission from the accretion disc
and subsequent response of the broad line region (BLR). The measurement of
$\tau$ is typically used to estimate the physical size of the BLR and is
combined with other measurements to estimate the black hole mass $M_{\rm BH}$.
A major difficulty with RM campaigns is the large amount of data needed to
measure $\tau$. Recently, \citet{2012MNRAS.427.2701F} introduced a new approach
to RM where the BLR light curve is sparsely sampled, but this is counteracted
by observing a large sample of AGN, rather than a single system.
The results are combined to infer properties of the sample of
AGN. In this letter we implement this method using a hierarchical
Bayesian model and contrast this with the results from the previous stacked
cross-correlation technique. We find that our inferences are more precise and
allow for more straightforward interpretation than the cross-correlation
technique.
\end{abstract}
galaxies:active --- methods: data analysis
\begin{keywords}

\end{keywords}

@@

The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated using
\begin{eqnarray}
X \\= \sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)
\end{eqnarray}

The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects.
\begin{eqnarray}
\textnormal{SCCF}(\tau) &=&
\frac{1}{N} \sum_{i=1}^N
\left(
\frac{\textnormal{CCF}_i(\tau)}{\int \textnormal{CCF}_i(\tau) \, d\tau}
\right)
\end{eqnarray}
In Figure~\ref{fig:ccf},
we show the stacked CCF from the 100 simulated AGN data sets.

>>>>

\begin{abstract}
Reverberation mapping (RM) is an important technique in studies of active
galactic nuclei (AGN). The key idea of RM is to measure the time lag $\tau$
between variations in the continuum emission from the accretion disc
and subsequent response of the broad line region (BLR). The measurement of
$\tau$ is typically used to estimate the physical size of the BLR and is
combined with other measurements to estimate the black hole mass $M_{\rm BH}$.
A major difficulty with RM campaigns is the large amount of data needed to
measure $\tau$. Recently, \citet{2012MNRAS.427.2701F} introduced a new approach
to RM where the BLR light curve is sparsely sampled, but this is counteracted
by observing a large sample of AGN, rather than a single system.
The results are combined to infer properties of the sample of
AGN. In this letter we implement this method using a hierarchical
Bayesian model and contrast this with the results from the previous stacked
cross-correlation technique. We find that our inferences are more precise and
allow for more straightforward interpretation than the cross-correlation
technique.
\end{abstract}

\begin{keywords}
galaxies:active --- methods: data analysis
\end{keywords}

@@

The cross-correlation function for a single object is defined as
in \citet{2012MNRAS.427.2701F}. For a lag bin between $\tau$ and $\tau + \delta$
the amount of cross correlation is calculated by looping over pairs of points
(one selected from the continuum data set, and another from the line data set),
and accumulating mass when the lag between the two points is between $\tau$
and $\tau + \delta$.
\begin{eqnarray}
X(\tau; \delta) =\\ \frac{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\left(y_i - \bar{y}\right)
\left(l_j - \bar{l}\right)
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
{\sum_{i=1}^{N_y}\sum_{j=1}^{N_l}
\mathds{1}\left((t_{l_j} - t_{y_i}) \in [\tau, \tau + \delta]\right)}
\end{eqnarray}
The denominator is the number of pairs of points that fall within the lag range
being considered, $[\tau, \tau + \delta]$.
The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects. In Figure~\ref{fig:ccf}, we show the stacked CCF
from our 100 simulated AGN data sets.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/example_posteriors.eps}
\caption{Samples from the posterior distribution for $\log_{10}(\bar{\tau})$
for three objects, each analysed separately with the single-object model. For
the first object, there is a moderate ``detection'' of a lag at about 10 days.
The second object yielded an upper limit, and the third object's lag was
not well inferred.
\label{fig:example_posteriors}}
\end{center}
\end{figure}
